First steps in synthetic algebraic geometry

### 2017-03-20 snippets/injective.tex
Remark on expectations of provability

\begin{rem}It's not known to me whether it's possible to intuitionistically
prove that any module can be embedded into a module which satisfies the internal
flabbiness criterion of Proposition~\ref{prop:internal-char-flabbiness}. This
would imply the corollary that any sheaf of modules can be embedded into a
flabby sheaf of modules. The naive candidates don't work: The
set~$\P_{\leq1}(F)$ doesn't admit a canonical module structure, and the free
module over that set is not flabby in general.

It's certainly not possible to intuitionistically prove that any module can be
embedded into an injective module, since it's consistent with Zermelo--Fraenkel
set theory that no nontrivial injective abelian groups
exist~\cite{blass:inj-proj-axc}.
\end{rem}

>>>>

\begin{rem}It's not known to me whether it's possible to intuitionistically
prove that any module can be embedded into a module which satisfies the internal
flabbiness criterion of Proposition~\ref{prop:internal-char-flabbiness}. This
would give an internal proof that any sheaf of modules can be embedded into a
flabby sheaf of modules. The naive candidates don't work: The
set~$\P_{\leq1}(F)$ doesn't admit a canonical module structure, and the free
module over that set is not flabby in general.

Since by the Godement construction the statement is true in many models of
intuitionistic logic, the sheaf toposes over topological spaces, and
furthermore the proof that the Godement construction yields a flabby sheaf is
intuitionistically valid,\footnote{In order for the Godement construction to
work in a intuitionistic metatheory, one has to tweak its definition a little
bit.  Instead of mapping an open subset~$U$ to~$\prod_{x \in U} \F_x$, one has
to map~$U$ to~$\prod_{x \in U} \P_{\leq1}(\F_x)$. This has the added advantage
that it works even if~$\F$ is not inhabited.} it's not unreasonable to believe
that such an intuitionistic proof is possible.

On the other hand, it's certainly not possible to intuitionistically prove that
any module can be embedded into an injective module, since it's consistent with
Zermelo--Fraenkel set theory that no nontrivial injective abelian groups
exist~\cite{blass:inj-proj-axc}.
\end{rem}
